Pomace: a Grappa for Non-Volatile Memory

### 2012-12-11 doc/nvm2013/paper.tex
final bib stuff

\paragraph{SSDs have a low request rate.} The fastest (cite) can
perform on the order of 1 million random reads per second, and many
are limited to less than 100K/s. In contrast, cores may be idle in
Grappa if each node cannot make 100 million random reads per second of
the global heap. Even the individual flash chips are slow: 50K/s (cite
micron).

\paragraph{SSDs have high overhead.} Commodity SSDs are usually treated
as normal disks---accesses must occur through the kernel, incurring a
high context switch overhead. Grappa depends on user-mode access to
the network layer. This capability has been explored in NVM research
(cite Moneta).

@@

While similar techniques have provided benefit in prior work in
restricted situations (cite), they depend on a sufficient request
density to each block to get a benefit. As datasets scale up, the
request density may decrease and the benefit of this technique may
decrease.

@@

\paragraph{PCM as Main Memory}
Much recent research has explored the use of PCM as a main memory
replacement. Grappa would easily be able to take advantage of such a
development. When a Grappa program references a low-locality program,
a prefetch request is issued for that data a few cycles before the
thread is context-switched in\cite{Nelson:hotpar2011}. A PCM-based
Grappa would do the same, but would issue the prefetches earlier to
cover the longer latency of PCM.

>>>>

\paragraph{SSDs have a low request rate.} The fastest~\cite{fusionio} can
perform on the order of 1 million random reads per second, and many
are limited to less than 100K/s. In contrast, cores may be idle in
Grappa if each node cannot make 100 million random reads per second of
the global heap. Even the individual flash chips are slow, on the order of 40K/s~\cite{micronFlash}.

\paragraph{SSDs have high overhead.} Commodity SSDs are usually treated
as normal disks---accesses must occur through the kernel, incurring a
high context switch overhead. Grappa depends on user-mode access to
the network layer. This capability has been explored in NVM research~\cite{caulfield:2012}.

@@

While similar techniques have provided benefit in prior work in
restricted situations~\cite{magt:2010,graphchi:osdi2012}, they depend on a sufficient request
density to each block to get a benefit. As datasets scale up, the
request density may decrease and the benefit of this technique may
decrease.

@@

\paragraph{PCM as Main Memory}
Much recent research has explored the use of PCM as a main memory
replacement. Grappa would easily be able to take advantage of such a
development. When a Grappa program references a low-locality program,
a prefetch request is issued for that data a few cycles before the
thread is context-switched in~\cite{Nelson:hotpar2011}. A PCM-based
Grappa would do the same, but would issue the prefetches earlier to
cover the longer latency of PCM.
